\cvsection{Selected Publications}

\vspace{3mm}

\hfill{\fontsize{8pt}{1em}\paragraphstyle \student\ denotes undergraduate co-authors.  \gradstudent\ denotes 
graduate student co-authors.}

\cvsubsection{Selected Journal Articles}

\begin{cvbib}

\cvbibitem{1}{annotating-www-journal}
\cvbibitem{2}{video-econf}
\cvbibitem{3}{evaluate-www-instruction}

\end{cvbib}

\cvsubsection{Selected Refereed Conference Papers}

\begin{cvbib}

\cvbibitem{4}{arts-coding-sigcse}
\cvbibitem{5}{mediascripting-sigcse}
\cvbibitem{6}{mediascripting-foss}
\cvbibitem{7}{web-mediation-alt}
\cvbibitem{8}{clios-worlds-alt}
\cvbibitem{9}{summarizing-links-alt}
\cvbibitem{10}{clios-assistants-alt}
\cvbibitem{11}{web-raveler-alt}
\cvbibitem{12}{blazing-trails-alt}
\cvbibitem{13}{satiric-alt}
\cvbibitem{14}{annotating-www-alt}
\cvbibitem{15}{in-class-course-webs}
\cvbibitem{16}{courseweaver}

\end{cvbib}

\cvsubsection{Books, Textbooks, Proceedings Editorship, Chapters in Books}

\begin{cvbib}

\cvbibitem{17}{grinnell-curricular-exemplar}
\cvbibitem{18}{edmedia2002-abstracts}
\cvbibitem{19}{edmedia2002-proceedings}
\cvbibitem{20}{experiments-in-java}
\cvbibitem{21}{multimedia-publishing-systems}
\cvbibitem{22}{electronic-multimedia-publishing}
\cvbibitem{23}{interactive-multimedia-publishing-systems}
\cvbibitem{24}{dags95}
\cvbibitem{25}{electronic-publishing}

\end{cvbib}

\cvsubsection{External Funding}

\begin{cventries}

\cventryGrant{CS1: Creative Computation in the Context of Art and Visual Media}{}{Fall 2016}
\cventryNote{Subaward of National Science Foundation Grant}
\cventryNote{\$3,000}

\cventryGrant{Reformulating Media Computation with Functional Programming, Scripting, and Design Principles}{}{May 2007 to July 2009}
\cventryNote{National Science Foundation Course, Curriculum, and Laboratory Improvement (CCLI) grant 0633090}
\cventryNote{Samuel A. Rebelsky (PI), Janet Davis (Co-PI), Matthew Kluber (Co-PI)}
\cventryNote{\$148,763}

\cventryGrant{Faculty Career Enhancement (FaCE)}{}{May 2006--August 2006}
\cventryNote{Associated Colleges of the Midwest (ACM)}
\cventryNote{Provided \$3000 to support attendance at SIGGRAPH and related conferences.}

\cventryGrant{Travel Grant}{}{Summer 2000}
\cventryNote{Iowa Computer Science Preparing Future Faculty Consortium using funds from a National Science Foundation program.}
\cventryNote{Supported student travel to EdMedia 2000 World Conference
  on Educational Multimedia and Hypermedia.}
\cventryNote{Approximately \$5,000.}

\cventryGrant{Smarter Kids Foundation}{}{Winter 1999}
\cventryNote{Approximately \$2,000}

\cventryGrant{Trailblazing Tools for the World Wide Web}{}{September 1998 to May 1999}
\cventryNote{The CRA Collaborative Research Environment for Women in Undergraduate Computer Science and Engineering Program}
\cventryNote{Samuel A. Rebelsky (Faculty Sponsor).  Rachel Heck, Sarah
  Luebke, Weichao Ma, and Hilary Mason (Students)}
\cventryNote{\$3,400}

\cventryGrant{Extending Introductory Computer Science with Algorithmic Multimedia}{}{July 1998 to June 2000.  Extended to June 2001.}
\cventryNote{NSF Instrumentation and Laboratory Improvement Grant DUE \#98-50546}
\cventryNote{Samuel A. Rebelsky (PI), John D. Stone (Co-PI), and Henry M. Walker (Co-PI)}
\cventryNote{\$33,600}

\end{cventries}
